%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer 2} % Job title
    {Microsoft - Xbox Game Pass} % Organization
    {Redmond, WA} % Location
    {Sept. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineering partnerships with Electronic Arts and Ubisoft to design and implement custom app-to-app communication mechanisms used to expand the Game Pass catalog with third party gaming content. Utilized gRPC, Windows protocol handlers, and registry to implement these integration solutions.} 
          \item{Improving the existing, ad-hoc, solutions: currently designing and implementing a COM-based, public-facing SDK to allow for more streamlined integration for past and future game catalog partners. Providing a contract to help third party publishers seamlessly integrate their content into the Xbox PC client with minimal additional Xbox engineering effort.}
          \item {Implemented both the frontend and backend of a new PC Game Pass upsell surface to be added into the Windows operating system's out-of-box experience, utilizing existing Microsoft infrastructure. Responsible for driving additional growth for the top-of-funnel PC subscriber count.} 
          \item{Increased robustness of Xbox PC client's infrastructure, leading to improvements in reliability, performance, and developer experience. Tasks included but not limited to: migrating the Xbox PC client to utilize the Hermes JavaScript engine, facilitating React Native Windows upgrades into the application, and onboarding the application to a new application monitoring platform (sentry.io).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Microsoft - Xbox Game Pass} % Organization
    {Redmond, WA} % Location
    {Nov. 2018 - Sept. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built and owned the subscription page for the PC client, the surface within the app used to drive user acquisition and retention.}
       	\item{Shipped numerous user facing features for the first version of the Xbox PC client, and features supporting the launch of PC Game Pass subscription.} 
	\item{Investigated and fixed critical bugs in preparation for the launch of the Xbox PC client and PC Game Pass at E3 2019.}	
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Program Manager} % Job title
    {Microsoft - Silicon, Graphics, and Media} % Organization
    {Redmond, WA} % Location
    {Sept. 2017 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item{Lead the team relationship with Qualcomm with a dev lead counterpart, tracked bugs and validation for incoming software, and managed code flow externally back to Qualcomm.}
      	\item{Kept work streams efficient and well documented to internal/external partners in order to develop and deliver a high quality product to our vertical teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
